---
title: "DMwR2 demo"
author: "Dr. J"
date: "11/15/2019"
output: 
  html_document:
  toc: true
  levels: 2
  number_sections: true
---

```{r setup }
knitr::opts_chunk$set(echo = TRUE)
library(DMwR2)
```

# Unsupervised learning: cluster analysis

```{r dataSets, echo=FALSE, include=FALSE}
data() # to see all the data sets available
```

## load the sales data set

```{r}
data(sales)
salesDF = sales
head(salesDF)
```


The sales data set consists of sale transaction reports.  there are just over 400,000 transactions.  The entries are 

Variable |  Description
---------|----------------
ID      | descripton    
Prod     | product ID
Quant    | quantity sold
Val     |  reported value of the transaction
Insp    | categorical variable: 'ok', 'fraud', 'unkn'

Only a small percentage of the transactions have been verified as either 'ok' or 'fraud.' 
The purpose of the study is to Use cluser analysis to identify the top 50 'unkn' transactions to be investigated for possible fraud

## Next step.... 
